Multi-channel Kondo model URG

### 2021-11-26 notes/multi-channel-urg.tex
calculated thermal entropy

The integration goes over positive energies only because of the \(1 - \hat n\) operator; the upper limit of the integration is chosen so as to make the denominator double, because this preserves the symmetry of the denominator and this is what happens in poor man's scaling. Performing the integration gives

@@

	\Delta H_1 = c^\dagger T \frac{1}{\omega^\prime - H_D} H_X \frac{1}{\omega^\prime - H_D} T^\dagger c = -\frac{1}{2}\frac{J^3 n(D) \rho K}{\omega - D/2 + J/4}\frac{1}{2}\left( -\frac{1}{4} \right) \sum_{k_1,k_2,\alpha_1,\alpha_2,b} S_d^b s^b_{\alpha_1 \alpha_2} c^\dagger_{k_1\alpha_1,l_2}c_{k_2 \alpha_2,l_2}\\
=\frac{1}{16}\frac{J^3 n(D) \rho K}{\omega - D/2 + J/4} \sum_{k_1,k_2,\alpha_1,\alpha_2} \vec{S_d}\cdot\vec{s}_{\alpha_1 \alpha_2} c^\dagger_{k_1\alpha_1,l_2}c_{k_2 \alpha_2,l_2}

@@

>>>>

The integration limits include only the positive energies, because of the \(1 - \hat n\) operator; the upper limit of the integration is chosen so as to make the denominator double, because this preserves the symmetry of the denominator. Performing the integration gives

@@

	\Delta H_1 = c^\dagger T \frac{1}{\omega^\prime - H_D} H_X \frac{1}{\omega^\prime - H_D} T^\dagger c = -\frac{1}{2}\frac{J^3 n(D) \rho K}{\omega - D/2 + J/4}\frac{1}{2}\left( -\frac{1}{4} \right) \sum_{k_1,k_2,\alpha_1,\alpha_2,b,l_2} S_d^b s^b_{\alpha_1 \alpha_2} c^\dagger_{k_1\alpha_1,l_2}c_{k_2 \alpha_2,l_2}\\
=\frac{1}{16}\frac{J^3 n(D) \rho K}{\omega - D/2 + J/4} \sum_{k_1,k_2,\alpha_1,\alpha_2,l_2} \vec{S_d}\cdot\vec{s}_{\alpha_1 \alpha_2} c^\dagger_{k_1\alpha_1,l_2}c_{k_2 \alpha_2,l_2}

@@

\section{Thermal entropy at \(T=0\)}
The thermal entropy at temperature \(T\) is given by
\begin{equation}\begin{aligned}
	S(T) = -k_B \sum_{n}P_n \ln P_n
\end{aligned}\end{equation}
where \(n\) sums over all eigenstates of the system. The state \(n\) is understood to have an energy \(E_n\). \(P_n\) is the probability to find the system in the state \(n\) from a canonical ensemble at temperature \(T\). This probability is given by
\begin{equation}\begin{aligned}
	P_n = \frac{e^{-\beta E_n}}{Z}
\end{aligned}\end{equation}
where \(Z = \sum_n d_n e^{-\beta E_n}\) and \(d_n\) is the degeneracy of the state \(E_n\). Substituting this gives for the entropy:
\begin{equation}\begin{aligned}
	S(T) = -k_B \sum_{n}\frac{e^{-\beta E_n}}{Z} \ln \frac{e^{-\beta E_n}}{Z}
\end{aligned}\end{equation}
Taking the limit of \(\beta \to \infty\) gives \(Z \to d_\text{gs}e^{-\beta E_\text{gs}}\):
\begin{equation}\begin{aligned}
	S(T) = -k_B \frac{d_\text{gs} e^{-\beta E_\text{gs}}}{d_\text{gs}e^{-\beta E_\text{gs}}} \ln \frac{e^{-\beta E_\text{gs}}}{d_\text{gs}e^{-\beta E_\text{gs}}} = k_B \ln d_\text{gs}
\end{aligned}\end{equation}
\begin{figure}[!ht]
	\centering
	\includegraphics[width=0.6\textwidth]{../numerics/entropy_comparison.pdf}
	\caption{Comparison of star graph zero temperature entropy with CFT/Bethe ansatz formula}
\end{figure}
